---
title: "MA 677 3.11"
author: "Jason Lu"
date: "2/10/2021"
output: pdf_document
---
(See paper for explanation in context of the problem)

Honestly, easier to think in alpha levels
We normally use alpha = 0.05 for significance, alpha is our critical value
  if p-value below, we reject H0
  if p-value above, we FTR H0
Now what if we use alpha = 0.01?
  We make it harder to reject H0 since our p-value now has to be "super significant"
  This makes it harder for a false alarm to happen, since we're only accepting super loud alarms
  However, it's easier for a missed opportunity
    If our p-value turns out to be 0.04, we would have rejected it under alpha = 0.05
    But since alpha = 0.01, we FTR H0
Now what if we use alpha = 0.10?
  We make it easier to reject H0 since our p-value can be higher than usual
  Easier for false alarms to happen since p-value can be 0.09 (which we would normally FTR H0)
  Harder for missed opportunities since we're accepting almost anything.

With this imagery of m as the critical value, it'll be easier to understand the explanation.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("bayesplot","knitr","arm","ggplot2","rstanarm","dplyr")
```

p = 0.6 and p = 0.8

```{r}
p = seq(0.4,1.0,by=0.01)
p.rej = 1 - pbinom(68,100,p)   # in black, 69 isn't here because we are taking out 68 with this code
p.rej2 = 1 - pbinom(73,100,p)  # in blue
# cbind(p,p.rej)
xlab = c("0.4","","0.5","","0.6","","0.7","","0.8","","0.9","","1")
ylab = c(".0","",".1","",".2","",".3","",".4","",".5","",".6","",".7","",".8","",".9","","1.0")

plot(p, p.rej, yaxt="n", type="l", main="Power Curve",yaxs="i",xaxs="i",xlim=c(0.4,1),ylim=c(0,1))
  xtick <- seq(0.4,1,by=0.05)
  ytick <- seq(0,1,by=0.05)
  axis(side=1,at=xtick,labels=xlab)
  axis(side=2,at=ytick,labels=ylab,las=2)
lines(p, p.rej2, col="blue")
rect(xleft=.6,xright=.8,ybottom=.05,ytop=.95)
```
In Figure 3.7, the x-axis is differing probabilities (0.6, 0.8, etc.) and the y-axis
is the cumulative probabilities. Black is for m=69 and Blue is for m = 73. The T1 error
rate at 5% is at the bottom whereas the T2 error rate at 5% is the 0.95 at the top.
We want to minimize both values so our m must be somewhere between these two numbers.
